Supplementary Information

### 2022-02-10 si/supplementary_information.tex
Added SI figures and bar and hinge gradients

% Referencing
\usepackage{cleveref}
\renewcommand{\theequation}{S\arabic{equation}}

@@

\section{Constraint coefficients}
The constraint coefficients are chosen to set comparable sizes for each term in the gradient of the BITSS potential,
\begin{equation}
  \grad{E_{tot}} = \sum_{\substack{i=1,2 \\ j\neq i}} \left[ 1 + 2 \kappa_e (E_i - E_j) \right] \grad{E_i} + 2 \kappa_d (d - d_0) \grad{d}.
\end{equation}

@@

\section{Parameter test}
The constant parameters $\alpha$ and $\beta$ still must be chosen.
To this end we have tested different parameter choices using the seven-particle cluster and cylindrical buckling examples.
\Cref{fig:paramtest} shows which choices lead to convergence and the speed at which they do.
The parameters $\alpha = 10$ and $\beta = 0.1$ are chosen for both converging quickly and being situated far from the regions of non-convergence.
Hence, this choice is unlikely to fail if the boudaries of the regions were to shift under different systems.

\begin{figure} \label{fig:paramtest}
  \includegraphics{fig/paramtest-a.pdf}%
  \includegraphics{fig/paramtest-b.pdf}%
  \caption{
    Speed of convergence of the BITSS method under different choices of parameters for (a) the seven-particle cluster, (b) cylindrical buckling.
    The speed is given by the number of evaluations of the gradient until the two states are separated by less than a thousandth of the initial separation.
    The combinations that do not converge to the transition state are shown in grey. 
    The chosen parameters are marked by a red star.
  }
\end{figure}

\section{Test potentials and gradients}

>>>>

% Referencing
\usepackage{cleveref}
\renewcommand{\theequation}{S\arabic{equation}}
\renewcommand{\thefigure}{S\arabic{figure}}

@@

\section{Constraint coefficients}
The constraint coefficients are chosen to set comparable sizes for each term in the gradient of the BITSS potential,
\begin{equation} \label{eq:gradBITSS}
  \grad{E_\text{BITSS}} = \sum_{\substack{i=1,2 \\ j\neq i}} \left[ 1 + 2 \kappa_e (E_i - E_j) \right] \grad{E_i} + 2 \kappa_d (d - d_0) \grad{d}.
\end{equation}

@@

\section{Parameter test}
The constant parameters $\alpha$ and $\beta$ still must be chosen.
To this end we have tested different parameter choices using the seven-particle cluster and cylindrical buckling examples.
\Cref{fig:paramtest} shows which choices lead to convergence and the speed at which this occurs.
The parameters $\alpha = 10$ and $\beta = 0.1$ are chosen for both converging quickly and being situated far from the regions of non-convergence.
Hence, this choice is unlikely to fail if the boudaries of the regions were to shift for different systems.

\begin{figure}
  \includegraphics{fig/paramtest-a.pdf}%
  \includegraphics{fig/paramtest-b.pdf}%
  \caption{\label{fig:paramtest}
    Speed of convergence of the BITSS method under different choices of parameters for (a) the seven-particle cluster, (b) cylindrical buckling.
    The speed is given by the number of evaluations of the gradient until the two states are separated by less than a thousandth of the initial separation.
    The combinations that do not converge to the transition state are shown in grey. 
    The chosen parameters are marked by a red star.
  }
\end{figure}

\section{Test potentials and gradients}
\begin{figure}
  \includegraphics{fig/BAHschematic.pdf}
  \caption{\label{fig:BAHschematic}
    Schematic of the bar and hinge model showing the relevent parameters for a single hinge element. $h_i$ and $\bm{\hat{n}}_i$ denote the height and unit normal of each triangle respectively.
  }
\end{figure}
To use L-BFGS minisation the gradients of the optimisation function must be known.
For the BITSS potential this is given by \cref{eq:gradBITSS}, but this still requires knowledge of the gradients of the system under consideration.
For the cylindrical buckling example we can obtain the gradient by considering each bond and hinge individually.
Using the schematic in \cref{fig:BAHschematic}, the gradient of the stretching energy of the bond between $\bm{x}_2$ and $\bm{x}_3$ is given by,
\begin{equation}
  \frac{\partial E^S}{\partial \bm{x}_2} = - \frac{\partial E^S}{\partial \bm{x}_3} = 
    2 k^S (r - r^0) (\bm{x_2} - \bm{x_3}).
\end{equation}
While the gradients of the bending energy of the hinge are,
\begin{align}
  \frac{\partial E^B}{\partial \bm{x}_1} &= k^B \sin(\theta - \theta^0) \frac{\bm{\hat{n}}_a}{h_a}, \\
  \frac{\partial E^B}{\partial \bm{x}_2} &= - k^B \sin(\theta - \theta^0) \left[\frac{\bm{\hat{n}}_a}{h_a} + \frac{\bm{\hat{n}}_a + \bm{\hat{n}}_b}{r}\right], \\
  \frac{\partial E^B}{\partial \bm{x}_3} &= - k^B \sin(\theta - \theta^0) \left[\frac{\bm{\hat{n}}_b}{h_b} + \frac{\bm{\hat{n}}_a + \bm{\hat{n}}_b}{r}\right], \\
  \frac{\partial E^B}{\partial \bm{x}_4} &= k^B \sin(\theta - \theta^0) \frac{\bm{\hat{n}}_b}{h_b}.
\end{align}

\section{DNEB speedtest}
